% -----------------------------------------------------------------------------
\section{Relationship to SBOL Visual 1.0}\label{sec:sbol1}
% -----------------------------------------------------------------------------

SBOL Visual 1.1 differs from SBOL Visual 1.0 in the following major ways:
\begin{itemize}
\item The relationship between diagrams and the SBOL data model is made explicit.
\item A number of requirements and best practices are specified for glyphs and diagrams, including:
	\begin{itemize}
	\item Glyphs include information on interior, bounding box, and recommended backbone alignment.
	\item Glyphs are required to have their bounding boxes contact the nucleic acid backbone.
	\item Nucleic acid diagrams now require the nucleic acid backbone line, and the number of lines allowed in various circumstances is constrained.
	% glyph overlaps needs to be handled be SEP
	%\item Glyphs are not allowed to overlap in bounding-box unless 
	\item Explicit statement of when a glyph can and cannot be used to represent a particular element of a diagram.
	\end{itemize}
\item Labels that name objects are distinguished from other types of textual annotation.
\item Explicit statement of which aspects of a symbol are {\em not} controlled.
\item Symbol variants are now supported.
\end{itemize}

In addition, the collection of glyphs have been expanded and modified in the following ways:
\todo[inline]{work this through in detail per the various SEPs}

%
%\begin{itemize}
%\item Ribonuclease Site has been assigned SO:0001977.
%\item 5' Sticky End Restriction Site has been assigned SO:0001975.
%\item 3' Sticky End Restriction Site has been assigned SO:0001976.
%\item Signature has been assigned SO:0001978.
%\end{itemize}
%
%% I have verified that there are all as desired.
%In addition, the following changes have been made to ontology links:
%\begin{itemize}
%\item The symbol for 5'UTR (SO:0000204) has been generalized from its former definition as Ribosome Entry Site (SO:0000139).
%\item User-defined component has been assigned a definition as Sequence Feature (SO:0000110).
%\item RNA stability element's can be defined as either SO:0001957 or SO:0001546.
%\item Restriction site can be defined as either SO:0001687 or SO:0000061.
%\item 5' Overhang Site and 3' Overhang Site were erroneously listed with their ontology terms exchanged; this has been fixed.
%\end{itemize}
%
